\documentclass[notitlepage,prd,article,floatfix,preprintnumbers,a4paper,nofootinbib,superscriptaddress]{revtex4-1}

\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath,amssymb}
\usepackage{amsfonts}
\usepackage{bm}
\usepackage[usenames,dvipsnames]{color}
\usepackage{amssymb}
\usepackage{psfrag}
\usepackage{times}
\usepackage[varg]{txfonts}
\usepackage[colorlinks, pdfborder={0 0 0}]{hyperref}
\usepackage{lineno}
\usepackage{verbatim}
\definecolor{LinkColor}{rgb}{0.75, 0, 0}
\definecolor{CiteColor}{rgb}{0.75, 0, 0}
\definecolor{UrlColor}{rgb}{0, 0, 0.75}
\hypersetup{linkcolor=LinkColor}
\hypersetup{citecolor=CiteColor}
\hypersetup{urlcolor=UrlColor}
\usepackage[utf8]{inputenc}
\usepackage{ulem}
\normalem
\hoffset -0.17in
\voffset 0.3in
\textheight 10in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Useful Definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{definitions}
\def\cw{\tilde{\omega}}
\def\CW{\tilde{\Omega}}
\def\lalapprox{\texttt{MMRDNS}}

% Numbers that may change from time to time
\def\CwFitCalibrationRegion{\red{0.99} }
\def\NumCalibrationPointsPlotted{\red{21} }
\def\NumCalibrationPoints{\red{61} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Erratum: \textit{Modeling ringdown: Beyond the fundamental quasinormal modes}\\
$[$Phys. Rev. D 90, 124032 (2014)$]$}

\author{L. T. London}
\affiliation{School of Physics and Astronomy, Cardiff University, The Parade, Cardiff, CF24 3AA, United Kingdom}
\affiliation{Center for Relativistic Astrophysics, School of Physics,
Georgia Institute of Technology, Atlanta, Georgia 30332, USA}
 \author{James Healy}
\affiliation{Center for Computational Relativity and Gravitation,
School of Mathematical Sciences, Rochester Institute of Technology, Rochester, New York 14623, USA}
 \author{Deirdre Shoemaker}
 \affiliation{Center for Relativistic Astrophysics, School of Physics,
 Georgia Institute of Technology, Atlanta, Georgia 30332, USA}


{\let\newpage\relax\maketitle}

%
\par While we currently present corrections and modifications to a subset of the tables, equations and figures in \cite{London:2014cma}, the work's core results and conclusions do not change: here, we modify the fitting formula, update plots containing overtones, and make a corrections to appropriate equations.
%
We have provided a public IPython notebook to accompany this erratum on github \cite{London:2016git}.
%
\par The algorithm used to generate Tables IV and V, as well as Equations (2-7) in \cite{London:2014cma} were found to be affected by an indexing error, through which the remnant black hole spin was erroneously equated with the remnant's mass.
%
In addition, the authors now choose to modify the fitting ansatz given by Equation (38) and (A2) such that overall factors of the symmetric mass ratio $\eta$ do not increase with overtone number.
%
This is motivated by the linearity of the $1^{\mathrm{st}}$ order \qnm{s} as $\eta \rightarrow 0$, and is consistent with Equation (35) of \cite{London:2014cma}.
%
Correcting the indexing error, and enforcing the more appropriate fitting ansatz for the overtones results in \eqns{eq:fit_fun_A220}{eq:fit_fun_A550}.
%
\input{fit_eqns}
%
\paragraph*{Related Figure Changes --} The changes above superficially affect Figures 7-9, 12 \& 14. Updated figures cannot be distinguished from those present in \cite{London:2014cma}; therefore they will not be amended here.
%
\paragraph*{Other Comments --} The equation just prior to Equation (32) is missing a factor of 2 in its exponent and thus should read $\cw^2_{lmn} = |\cw_{lmn}|^2 \, e^{-2\varphi_{lmn}}$.
%
The first line of Equation (32) should contain $\cw^2_{lmn}$ not $\cw^2_{nlm}$.
%
In \eqns{eq:fit_fun_A220}{eq:fit_fun_A550}, the authors choose to omit the $(l,m,n) \in \{ (5,4,0), \; (2,2,2) \}$ \qnm{s} due to data quality concerns.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
\bibliographystyle{ieeetr}
\bibliography{erratum.bib}
\end{document}
